
\item A coin is tossed 100 times. Using the appropriate approximating distribution, estimate the probability that
a) exactly 46 heads are thrown
b) between 48 and 59 heads (inclusively) are thrown.
\itemI obtain a hand of 13 cards. Calculate the probability of
i) obtaining 2 aces.
ii) obtaining 2 aces and 2 kings.
iii) obtaining 2 aces or 2 kings.

\item A computer chooses a number at random n times from the set {1, 2, 3, 4, 5} (with replacement). Let S denote the sum of the numbers chosen. Show that
E(S) = 3n and Var(S) = 2n.

\itemLet Y=aX+b. Prove that i) E(Y)=aE(X)+b, ii) Var(Y)=a2Var(X).

\itema) Suppose X has a geometric distribution with parameter p. From the standard interpretation of the geometric distribution, conditioning on whether X=1 or not and using the memoryless property of the geometric distribution
i)calculate E(X)
ii)calculate Var(X). [Hint: first calculate E(X2)].

\item The probabilities with which Liverpool win, draw or lose a premier league match are 0.5, 0.3 and 0.2, respectively. Calculate the probability that in 8 matches
i)Liverpool lose 2 matches.
ii)Liverpool win 5 matches and draw 2.
\item % \frametitle{Review Question 5 :  Probability}
If A and B are events such that $P(A|B^c) = 2P(A|B)$ and $P(B^c) = 2P(B)$.
(The event $B^c$ is the complement of event B.) Compute the probability: $P(B^c|A)$ 
\begin{framed}
\begin{itemize}
\item Complement events: $P(B^c) = 1 - P(B)$. Also we are told $P(B^c) = 1-P(B)= 2P(B)$
\item Necessarily $1 = 3P(B)$. Therefore $P(B) = 1/3$ and  $P(B^c)=2/3$
\item Total Probability: $P(A) = P(A \mbox{ and } B) + P(A \mbox{ and } B^c)$
\end{itemize}
\end{framed}
