\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{Maths Resource} \rhead{Tutorial Sheet B} \chead{Discrete Random Variables} %\input{tcilatex}
\begin{document}

\begin{enumerate}

\item A fair coin is tossed four times.
Let X denote the longest string of heads.

Find the distribution and expectation of X.


% (The game is fair, favourable, or unfavourable to the player if E(X) = 0,E(X) > 0 or E(X) < 0 respectively)


\item A fair coin is tossed four times.
Let X denote the longest string of heads.
Find the distribution and expectation of X.
\item 
A fair coin is tossed until a head or five tails occurs.
Find the expected number E of tosses of the coin.

\item A coin is weighted so that $P(H) = 0.75$ and $P(T ) = 0.25$

The coin is tossed three times. Let X denote the number of
heads that appear.
\begin{enumerate}[(a)]
\item  Find the distribution f of X.
\item  Find the expectation E(X).
\end{enumerate}

\item 
A box contains two gold balls and three silver balls. 
\begin{itemize}
\item You are allowed to choose
successively balls from the box at random. 
\item You win 1 dollar each time you
draw a gold ball and lose 1 dollar each time you draw a silver ball. 
\item After a
draw, the ball is not replaced.
\end{itemize} Show that, if you draw until you are ahead by
1 dollar or until there are no more gold balls, this is a favorable game.


\end{document}