\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MA4413 2013} \rhead{Mr. Kevin O'Brien}
\chead{Midterm Assessment 1 }
%\input{tcilatex}

\begin{document}

\section*{Attempt ALL questions}

\subsection*{Question 1 Probability []}
%-----------------------------------%

\textbf{Description of the Experiment}
\begin{itemize}

\item Suppose we have two bags, each containing 2 marbles. 

\item One bag has 2 red marbles and
the other has a red marble and a yellow marble. 
You pick a bag at random and then pick
one of the marbles in that bag at random. 

\item When you look at the marble, it is red. 
You
now pick the second marble from that same bag.
\end{itemize} 
\textbf{Questions}
\begin{itemize}

\item[(a)]  Write down the sample space for this experiment, where the outcomes are the ordered pairs of drawn marbles.

\item[(b)] What is the probability that this marble
is also red? Select one of the options below, with a justification for your answer.
You may justify your answer by references to sample points.
\end{itemize}
\textbf{Options for part b}
\begin{center}
\begin{multicols}{4}
\begin{itemize}

\item 1/4

\item 1/3

\item 2/3

\item  1/2
\end{itemize}
\end{multicols}
\end{center}


\bigskip
%-----------------------------------%
\subsection*{Question 2 Descriptive Statistics []}

Consider the following data set of seven numbers:

\begin{center}
\textbf{\texttt{18, 14,  8, 15, 17,  9, 10 }}
\end{center}
% 4 Marks

\noindent For this sample, compute the following descriptive statistics:
\begin{itemize}
%
\item[a.]  The median,

\item[(a)]  The mean,

\item[(b)]  The median,

\item[(c)]  The standard deviation.
\end{itemize}

\newpage
