
%===============================================================%






\subsection{Question - With Solution}


A driver passes through 3 traffic lights. The chance he/she will stop at the first is 1/2 , at the second 1/3 and at the third ¼ independently of what happens at any of the other lights. What is the probability that

\begin{enumerate}
\item    the driver makes the whole journey without being stopped at any of the lights

\item   the driver is only stopped at the first and third lights

\item  the driver is stopped at just one set of lights.
\end{enumerate}

P[F] = 0.5           P[Fc] = 0.5            P[S] = 0.333        P[Sc] = 0.666

P[T] = 0.25         P[Tc] = 0.75





Probability of not getting stopped at all three lights


P[0] =P[Fc]P[Sc]P[Tc] = 0.50.6660.75 = 0.25



Probability of only getting stopped at first  lights


P[F only] = P[F]P[Sc]P[Tc] = 0.50.6660.75 = 0.25


Probability of only getting stopped at second lights


P[S only] =P[Fc]P[S]P[Tc] = 0.50.3330.75 = 0.125








Probability of only getting stopped at third  lights

P[T only] =P[Fc]P[Sc]P[T] = 0.50.6660.25 = 0.083


Probability of getting stopped at one lights only 


P[1 only] =P[F only]+P[S only]+ P[T only]


P[1 only] = 0.125 + 0.25 + 0.083 = 0.458






\subsection{Exercise : Probability of Two Dice Rolls}
A pair of dice is thrown. Let X denote the minimum of the two numbers which occur.
Find the distributions and expected value of X.








Question 3
c) Calculate the probability of obtaining exactly 2 sixes when I roll a die 5 times.
(4 marks)

\noindent \textbf{Worked Example}\\
A worker-operated machine produces a defective item with probability 0.01 if the worker follows the machine’s operating instructions exactly, and with probability 0.04 if he does not. If the worker follows the instructions 90\% of the time, what is the probability that an item produced by the machine, selected at random, will be defective?







\textbf{Dice Questions}
\begin{enumerate}

%----------------------------------------------------------%
\item Based on the following information, express $q$ in terms of $p$ and $r$.
\begin{itemize}
\item Suppose that 4 numbers have a mean of $p$
\item Suppose that five other numbers have a mean of $q$.
\item These nine numbers have a mean of $r$.
\end{itemize}


\end{enumerate}

\section*{May 2013 Question 4 Probability}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline  & within $W$ & outside $O$ & Totals \\ 
\hline Correct time $C$ & 83 & 51 & 134 \\ 
\hline Delayed $D$ & 24 & 12 & 36 \\ 
\hline Totals & 107 & 63 & 170 \\ 
\hline 
\end{tabular} 
\end{center}\begin{itemize}
\item Probability of departing at correct time
\[P(C) = 107/170\]
\item Probability of being delayed and flying outside europe 
\[P(D  \mbox{ and } O) = 12/170\]
\item Probability of 
\[P() \]
\item Probability of 
\[P() \]
\item Probability of 
\[P() \]
\end{itemize}
