
 
%--------------------------------------------------------------------------------------%

Sample Space: This is the set of all possible outcomes of a random experiment, and is denoted $S$. An element in $S$ is called a sample point.
Each outcome of a random experiment corresponds to a sample point.
Find the sample space for the experiment of tossing a coin (a) one and (b) twice.
(a) There are two possible outcomes: heads or tails.
Thus
S= {H,T}where $H$ and $T$ represent head and tail respectively.
(b) There are four possible outcomes, which are pairs of heads and tails.
Thus S= {HH,HT,TH,TT} 
%--------------------------------------------------------------------------------------%
Considering a coin toss experiment. A fair coin is tossed three times.
Let X be the random variable that counts the number of heads in each sample point.
P(X\leq 1)
P(X\>1)
p(0<X<3)
Set of Eligible outcomes = \{1,2\}

%--------------------------------------------------------------------------------------%

A production line produces 1000-ohm resistors that have 10\% tolerance.
Let $X$ denote the resistance of a resistor.
Assuming that X is a normally distributed random variable with mean 1000 and variance 2500, find the probability that a randomly selected resistor will be rejected.
Solution:
Let A be the event that a resistor is rejected.
P(A)  = P(X \leq 900) + P( X \geq 1100)
P(X \leq 900)
Z value
Z_{900} = { 900 - 1000\over 50} = -2
X_{1100} = { 1100 - 1000\over 50} = 2
Probability of being rejected is 0.045 (i.e. 4.5 \%)

