	\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{Maths Resource} \rhead{Tutorial Sheet} \chead{Probability} %\input{tcilatex}

\begin{document}
\begin{enumerate}
	\item I pick 3 cards from a pack of 52. Calculate the probability that 
	i)	I pick exactly one spade
	ii)	I pick at least one spade
	iii)	I pick exactly one spade, given that I pick at least one spade.
	
\item The probability that a new born child is a boy is 0.51. Calculate the probability that in a family with 3 children
	i)	there are two girls and one boy
	ii)	all the children are boys, given that the eldest and the youngest child are of the same sex.
	
\item	A coin is thrown 4 times. Calculate 
	i)	The probability of throwing 4 heads
	ii)	The probability of throwing 3 heads 
	iii)	The probability of throwing 3 heads, given that the result of the first roll is tails.
	

	\item A machine is composed of 3 components, which function independently of each other with probabilities p1, p2 and p3, respectively. Calculate the probability that the machine works when
	a)	the machine only works when all the components are working
	b)	the machine works when at least one of the components works.
	
	\item  A die is thrown twice. A is the event that the sum is 7. B is the event that the first die roll results in a 1. C is the event that the second die roll results in a 6. 
	i)	Are the events A, B and C independent?
	ii)	Are the events A, B and C pairwise independent?
\item A coin is tossed until it falls on the same side twice in a row.
\begin{itemize}
	\item[(i)] Define the set of elementary events of such an experiment.
	\item[(ii)]  Calculate the probability that the coin is thrown exactly 5 times.
	\item[(iii)]  Calculate the probability that the number of throws is even.
\end{itemize}
%--------------------------------------------------%	
\item	In a newspaper on average 1 in 10 000 characters is incorrectly printed. Suppose the paper contains 50 000 characters. Calculate the exact probability that 
 \begin{itemize}
\item[(i)]	no printing errors are made
\item[(ii)]	at least 3 errors are made
 \end{itemize}	
	Using the appropriate approximation, estimate these two probabilities. 
%--------------------------------------------------%	

\item 	Suppose X has the following cumulative distribution function. F(x)=0, for x≤0, 
	F(x)=1, for x≥5 and F(x) = x3/125 for 0≤ x ≤ 5. Derive E(X) and Var(X).
	
	
	
\item  Suppose calls come into a call centre randomly at a rate of one per 30 seconds.
	i) What is the distribution of the time to the second call?
	ii) Using this distribution, calculate the probability that the second call arrives within a minute. 
	iii) Using the appropriate discrete distribution, calculate the probability that at least 2 calls are received in a minute (note this probability has to be the same as above).
	iv) What is the exact distribution of the time to the 200th call?
	v) Using the central limit theorem, give the normal distribution which approximates the distribution from iv).
	vi) Using your answer from v), estimate the probability that the time to the 200th call is less than 102 minutes.
	
\item A coin is tossed 100 times. Using the appropriate approximating distribution, estimate the probability that
	a) exactly 46 heads are thrown
	b) between 48 and 59 heads (inclusively) are thrown.
\item	I obtain a hand of 13 cards. Calculate the probability of
	i) obtaining 2 aces.
	ii) obtaining 2 aces and 2 kings.
	iii) obtaining 2 aces or 2 kings.
	
\item A computer chooses a number at random n times from the set {1, 2, 3, 4, 5} (with replacement). Let S denote the sum of the numbers chosen. Show that
	E(S) = 3n and Var(S) = 2n.
	
\item	Let Y=aX+b. Prove that i) E(Y)=aE(X)+b, ii) Var(Y)=a2Var(X).
	
\item	a) Suppose X has a geometric distribution with parameter p. From the standard interpretation of the geometric distribution, conditioning on whether X=1 or not and using the memoryless property of the geometric distribution
	i)	calculate E(X)
	ii)	calculate Var(X). [Hint: first calculate E(X2)].
	
\item	The probabilities with which Liverpool win, draw or lose a premier league match are 0.5, 0.3 and 0.2, respectively. Calculate the probability that in 8 matches
	i)	Liverpool lose 2 matches.
	ii)	Liverpool win 5 matches and draw 2.
\item % \frametitle{Review Question 5 :  Probability}
If A and B are events such that $P(A|B^c) = 2P(A|B)$ and $P(B^c) = 2P(B)$.
(The event $B^c$ is the complement of event B.) Compute the probability: $P(B^c|A)$ 
\begin{framed}
\begin{itemize}
\item Complement events: $P(B^c) = 1 - P(B)$. Also we are told $P(B^c) = 1-P(B)= 2P(B)$
\item Necessarily $1 = 3P(B)$. Therefore $P(B) = 1/3$ and  $P(B^c)=2/3$
\item Total Probability: $P(A) = P(A \mbox{ and } B) + P(A \mbox{ and } B^c)$
\end{itemize}
\end{framed}

\item I pick 3 cards from a pack of 52. Calculate the probability that 
\begin{enumerate}[(i)]
\item I pick exactly one spade
\item I pick at least one spade
\item I pick exactly one spade, given that I pick at least one spade.
\end{enumerate}

\item The probability that a new born child is a boy is 0.51. Calculate the probability that in a family with 3 children
\begin{enumerate}[(i)]
\item there are two girls and one boy
\item all the children are boys, given that the eldest and the youngest child are of the same sex.
\end{enumerate}

\item 
Consider a couple that has two children. Treating the gender of the children as an \textit{\textbf{ordered pair}} outcome of a random experiment, the sample space is 
\[\boldsymbol{S} = \{ (b,b), (b,g), (g,b), (g,g)\}.\]
Let us assume that each sample point is \textit{\textbf{equiprobable}}, with probability 0.25 for each sample point.
Find the probability $p$ that both children are girls if it is known that: 

\begin{itemize}
\item[(a)] at least one of the children is a girl,
\item[(b)] the older child is a girl. 
\end{itemize}

\item 
If two events A and B have the following probabilities $P(A) = 0.3$, $P(B) = 0.6$, $P(A|B) = 0.2$

\begin{itemize}
\item[(i)] Are A and B independent? Justify your answer.
\item[(ii)] Are A and B mutually exclusive? Justify your answer.
\item[(iii)] Calculate $P(A \cup B)$.
\end{itemize}





\item Tickets numbered 1 to 20 are mixed up and then a ticket is drawn at random. What is the probability that the ticket drawn has a number which is a multiple of 3 or 5

\item 
Which are the following pairs of events are mutually exclusive?

i.
Two dice are thrown: A is the event the sum is 10, B is the event the sum is 11


ai.
A hand of two cards is dealt: A is the event that the hand includes at least one red card, B is the event that the hand includes at least one black card.


bi.
student is chosen from the class at random: A is the event that the student is female, B is the event that a student is left-handed.






\begin{framed}


Solution

\begin{itemize}
\item[(i)] is mutually exclusive. cant throw 10 and 11 in same throw of two dice.


\item[(ii)] not mutually exlusive: can have one red card and one black card.


\item[(iii)] not mutually exclusine: can have a lefthanded female
\end{itemize}
\end{framed}
%================================================================================%




\end{document}
