



\section{Confidence Interval examples}



%--------------------
\subsection{Example}
A random sample of 15 observations is taken from a normally distributed population
of values. The sample mean is 94.2 and the sample variance is 24.86.
Calculate a 99\% confidence interval for the population mean.


\noindent \textbf{Solution}
$t_(14,0.005) = 2.977$
99\% CI is $94.2 \pm 2.977 \sqrt{24.86/15}$ \\i.e. $94.2 \pm 3.83$ \\i.e. $(90.37,98.03)$


\subsection{Example 1: paired T test}

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
X & 5.20 & 5.15 & 5.17 & 5.16 & 5.19 & 5.15\\ \hline 
Y & 5.20 & 5.15 & 5.17 & 5.16 & 5.19 & 5.15\\
\hline
\end{tabular}
\end{center}

\subsection{Example 2}

Seven measurements of the pH of a buffer solution gave the
following results:

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
5.12 & 5.20 & 5.15 & 5.17 & 5.16 & 5.19 & 5.15\\
\hline
\end{tabular}

Task 1: Calculate the 95\% confidence limits for the true pH
utilizing $R$.


Solution. We are using Student t distribution with six degrees of
freedom and the following code gives us the confidence interval
for this problem.
\begin{verbatim}
>x <- c(5.12, 5.20, 5.15, 5.17, 5.16, 5.19, 5.15)
>n =length(x)
>alpha =0.05
>stderr =sd(x)/sqrt(n)
>LB=mean(x)+qt(alpha/2,6)* stderr
>UB=mean(x)+qt(1-alpha/2,6)* stderr
>LB
#[1] 5.137975
>UB
#[1]5.187739
\end{verbatim}

\subsection{Example 3} Ten replicate analyses of the concentration
of mercury in a sample of commercial gas condensate gave the
following results (in ng/ml) :

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
23.3 & 22.5 & 21.9 & 21.5 & 19.9 & 21.3 & 21.7 & 23.8 & 22.6 &
24.7\\
\hline
\end{tabular}

Compute 99\% confidence limits for the mean.
%http://www.stats.gla.ac.uk/steps/glossary/hypothesis_testing.html


%-----------------------
\subsection{Using Tables for the $t$-Distribution}

Degress of freedmom n-1

\begin{itemize}
\item For values between 31 and 40 we can use degrees freedom = 40

\item For samples sizes between 41 and 60, we can use degrees of freedom 60

\item For samples sizes between 61 and 120, we can use degrees of freedom 120

\item For samples larger than 120, we can use $\infty$
\end{itemize}

%------------------------------------------------------------------------------%

\noindent \textbf{Confidence Interval for a Mean (Small Sample)}
\begin{itemize}
\item The mean operating life for a random sample of $n = 10$ light bulbs is $\bar{x} = 4,000$ hours, with the sample
standard deviation $s = 200$ hours. \item The operating life of bulbs in general is assumed to be approximately normally distributed.\item
We estimate the mean operating life for the population of bulbs from which this sample was taken, using a 95 percent
confidence interval as follows:

\[4,000\pm(2.262)(63.3)  = (3857,4143)\]

\item The point estimate is 4,000 hours. The sample standard deviation is 200 hours, and the sample size is 10. Hence \[S.E(\bar{x} ) = { 200 \over \sqrt{10}} = 63.3\]

\item From last slide, the t quantile with $df=9$ is 2.262.
\end{itemize}


%------------------------------------------------------------------------%


% -- Lecture 8B
% -- Revise the Tables
% -- Sample Size Estimation for mean
% -- Example SSE for mean
% -- SSE for Proportion
% -- Example SSE for proportion
% -- Paired Test



\item Your company produces injected mouldings for rotary arms. The company claims that less than 2% of all product produced is defective. A random sample of 100 parts revealed that 4 parts were defective. 

Using a 5% level of significance is there evidence to close the line down? Justify your decision.

%----------------------------------------------------------------------% 
% 2002 - Q3

\item Two injection moulding machines in separate plants manufacture battery
connectors for the same client company.  The critical parameter is the mean cushion distance.  A random sample of 4 products from each company was tested and the results recorded as follows:

Factory 1Factory 2
Sample (mm) Measurements38,     38.5
39.5,  40(35.5)  (36.5)
(37)     39
Mean cushion distance3937
Standard DeviationUnknownUnknown

%------------------------------------------% 
You are required to test the hypothesis that there is no statistical difference between the two populations.  You may assume a 10% probability of a Type 1 error.

\item The sample variance for population one is 0.83 and sample variance for population two is 2.17.  Does the data provide sufficient evidence to support the hypothesis that the populations are homogenous.  Use a 5% level of significance and indicate clearly all calculations made.




%----------------------------------------------------------------------% 
% 2002 - Q5

\item A production manager wanted to establish if there was a relationship between the number of hours recorded for a manufacturing cell and the number of units produced in the cell.  A random sample of 7 different times and their corresponding number of units produced were recorded as follows:


XY
HoursCell Prod.
125
236
347
4610
579
6912
71012

xy = 407x2 = 295x = 41y = 61

(a) You are required to 
i.Draw a scattergram and comment on its features
ii.Find the regression equation and plot the regression equation on scattergram


The data was entered into Minitab and the following outputs were generated

\begin{verbatim}
PredictorCoefSE CoefTP
Constant3.40630.60415.640.002
Hours0.906250.093059.740.000

S= 0.6892R-Sq = 95.0%R-Sq(adj) = 94.0%
\end{verbatim}

%------------------------------------------%

(b) You are requested to explain how the T-value of 9.74 was calculated and to 
interpret the corresponding P value of 0.000

%------------------------------------------%

(c)Fill in the blanks from the following table and explain the relationship between F value of 94.85 and the T-value of 9.74 in section (b)

Analysis of Variance
SourceDFSSMSFP
Regression145.05445.05494.850.000
Residual Error5xxxxx
Total647.429
\end{enumerate}

\end{document}
