



\subsection*{Question 4}
A friend claims that he can pass a particular game in 4 hours or less (on average). We wish to test this hypothesis at the 10\% level of significance. Your friend plays the game on 6 different occasions: his average completion time is 4.6 hours and the standard deviation is 0.5 hours. \\[-0.2cm]

{\bf(a)} State the null and alternative hypotheses. \quad {\bf(b)} What is the critical value? \quad {\bf(c)} Calculate the test statistic and provide your conclusion. \quad {\bf(d)} Between what two values does the p-value lie? (note: the p-value cannot be calculated exactly using the t-tables)



\subsection*{Question 5}
A die is rolled 80 times and we count 18 sixes. We wish to test the hypothesis that the die is fair (note: if this is the case, the proportion of sixes is $p = \frac{1}{6}$). \\[-0.2cm]

{\bf(a)} State the null and alternative hypotheses. \quad {\bf(b)} If we wish to test at the 5\% level of significance, what is the critical value? \quad {\bf(c)} Calculate the test statistic and provide your conclusion.



	\newpage\subsection*{Question 5}
	Consider the following two types of heat sink used for the purposes of CPU cooling:\\[-0.4cm]
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			&&\\[-0.3cm]
			& Type 1 & Type 2 \\
			\hline
			&&\\[-0.3cm]
			number tested      & 50 & 50 \\
			mean CPU temperature   & 40.1  & 34.8 \\
			standard deviation &  2.5 & 1.1 \\[0.1cm]
			\hline
		\end{tabular}
	\end{center}
	
	{\bf(a)} Identify the parameter of interest. \quad {\bf(b)} Calculate a 95\% confidence interval for the parameter and comment. \quad {\bf(c)} How large a sample is required to reduce the \emph{margin of error} in the previous confidence interval to $\pm 0.4$? (note: assume that $n_1 = n_2$)
	
	

	
\subsection*{Question 6}
A group of 9 computer science students were randomly selected and asked how many hours they spent gaming last week. The average time was found to be 6.4 hours and the standard deviation was 2.2 hours.
\begin{itemize}
	\item[{\bf(a)}] Calculate a 95\% confidence interval for $\mu$. \item[{\bf(b)}] Calculate a 99\% confidence interval for $\mu$.
\end{itemize}






\subsection*{Question 7}
Last year 30\% of applicants to a graduate programme failed the aptitude test. This year 100 graduates applied - 25\% of these failed the test.\\[-0.2cm]

{\bf(a)} We wish to test the hypothesis that the quality of applicants has not changed since last year - what are the null and alternative hypotheses? \quad {\bf(b)} If we are testing at the 1\% level, what is the rejection region? \quad {\bf(c)} Based on the data, calculate the test statistic and provide your conclusion.





\subsection*{Question 7}
Guinness set their bottle-filling machine to put 33cl into each bottle. A sample of 5 bottles were selected at random and measured. The volumes in cl were as follows:\\[-0.2cm]
\begin{center}
	\begin{tabular}{|ccccc|}
		\hline
		&&&&\\[-0.3cm]
		34.1  & 33.5 & 32.8 & 33.1 & 32.5\\[0.1cm]
		\hline
	\end{tabular}
\end{center}


{\bf(a)} Calculate the sample mean and standard deviation. \quad {\bf(b)} Calculate a 95\% confidence interval.  \quad {\bf(c)} Based on the confidence interval, does it appear that the machine is working correctly?












%=====================================================================%
\end{document}