
\documentclass[]{article}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{color}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}

\section*{Hypothesis Testing : Tutorial Sheet C}

\begin{enumerate}


\item The typing speeds for one group of eight IT students were recorded both at the beginning of
year 1 of their studies and at the end of year 4. The results (in words per minute) are given
below:
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|} \hline 
  Subject & A& B& C& D& E& F& G& H \\ \hline
Year 1& 173& 183& 176& 191& 184& 177& 175& 177 \\ \hline
Year 4& 172& 184& 180& 190& 191& 187& 181& 183 \\ \hline
\end{tabular}
\end{center}


\item 
% Hypothesis Testing (9 Marks)
In a computer hardware manufacturing plant, machine X and machine Y
produce identical components. The management investigate whether or
not there is a difference in the mean diameter of the components from
both machines.
\begin{itemize}
\item A random sample of 144 components from machine X had a mean of
36.38 mm and a standard deviation of 3.0 mm.
\item  A random sample of 225 components from machine Y had a mean of
36.88 mm and a standard deviation of 2.8 mm.
\end{itemize}
Compute a 95\% confidence interval for the difference in means.What is your conclusion for this procedure? Justify your
answer.
\item Two similar machines are making components of a particular length in mm.
Compute a 95\% confidence interval for the difference in average length between the components

The results for each machine are
\begin{itemize}
\item Machine A: $\{23.7, 23.0, 22.2, 24.0, 21.2, 23.1, 27.1, 24.0\}$ $(n_1 = 8)$
\item Machine B: $\{23.4, 15.3, 30.9, 18.8, 25.3, 25.2, 32.1\}$ ($n_2 = 7)$
\end{itemize}

You may assume that the populations are normal with variance 9 for the first machine and 16 for
the second machine.


\end{enumerate}
\end{document}