
\newpage
\section{KB Tutorial 6}






\subsection*{Question 4}
{\footnotesize({\bf Note}: this is not a queueing theory question. It is a generalisation of a question which appears on Tutorial2)}\\[0.1cm]
There are two possible routes to a particular location. You take $R_1$ 80\% of the time and $R_2$ 20\% of the time. We assume that travel time has an exponential distribution and, furthermore, the average travel time is 0.25 hours if you take $R_1$ and 0.5 hours if you take $R_2$.\\[-0.2cm]

{\bf(a)} Calculate the probability that the journey takes more than 0.5 hours for each of the routes, i.e., $\Pr(T > 0.5\,|\,R_1)$ and $\Pr(T > 0.5\,|\,R_2)$ respectively. \quad {\bf(b)} Calculate $\Pr(T > 0.5)$. (hint: law of total probability) \quad {\bf(c)} Given that $T>0.5$ hours, what is the probability that you used $R_1$? (i.e., calculate $\Pr(R_1\,|\,T>0.5)$) \quad {\bf(d)} Derive a general expression for $\Pr(R_1\,|\,T>t)$ and evaluate it at $t=0.25$, $t = 1$ and $t = 2$ respectively. Interpret the results.




\subsection*{Question 5}
Let $X \sim \text{Normal}(\mu=10,\sigma=2)$. Calculate the following:\\[-0.2cm]

{\bf(a)} $\Pr(X>10)$. \quad {\bf(b)} $\Pr(X<3)$. \quad {\bf(c)} $\Pr(X>8.4)$. \quad {\bf(d)} $\Pr(6<X<14)$. \quad {\bf(e)} The value of $x$ such that $\Pr(X>x)$ = 0.3. \quad {\bf(f)} The value of $x$ such that $\Pr(X>x)$ = 0.8.



\subsection*{Question 6}
Assume that speeds of cars on a motorway have a normal distribution with mean 115km/hr and standard deviation 4km/hr.\\[-0.2cm]

{\bf(a)} Draw a rough sketch of the distribution. \quad {\bf(b)} $\Pr(X>120)=$ ? \quad {\bf(c)} $\Pr(X<100)=$ ? \quad {\bf(d)} $\Pr(100<X<110)=$ ? \quad {\bf(e)} 1\% of drivers travel above what speed?







\subsection*{Question 7}
For \emph{any} normal variable $X \sim \text{Normal}(\mu,\sigma)$:\\[-0.2cm]

{\bf(a)} Show that $\Pr(\mu-3\,\sigma<X<\mu+3\,\sigma) = 0.997$. \quad {\bf(b)} Find a value for $k$ such that $\Pr(\mu-k\,\sigma<X<\mu+k\,\sigma) = 0.95$. \quad {\bf(c)} Find $k$ such that $\Pr(\mu-k\,\sigma<X<\mu+k\,\sigma) = 0.99$. \quad {\bf(d)} Show that $\Pr(X>\mu+1.64\,\sigma) = 0.05.$

