%Progress 7/15
\subsection*{Question 3 Discrete Random Variable [2 Marks]}
The probability distribute of discrete random variable $X$ is tabulated below. There are 5 possible outcome of $X$, i.e. 1, 2, 3, 4 and 5.
{
\large
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
$x_i$  & 1 & 2 & 3 & 4 & 5  \\\hline
$p(x_i)$ & 0.30 & 0.20 & 0.20 & 0.10 & 0.20 \\
\hline
\end{tabular}
\end{center}
}
\begin{itemize}
%\item[a.]  Compute the value of $k$.
\item[(a)]  What is the expected value of X?
\item[(b)]  Compute the value of $E(X^2)$,
\item[(c)]  Compute the variance of $X$.
\end{itemize}
\bigskip
\section*{Question 4 Poisson Distribution [3 Marks]}

\begin{itemize}
\item Suppose that, for a Poisson random variables $X$, the expected number of occurences in a one hour time period is 2. 


\item Furthermore, the probability of exactly one occurence in a one
 hour time period is $0.2706$.

\item Based on this information, answer the following questions.
\end{itemize}
\noindent{\textbf{Questions}}
\begin{itemize}
\item[(a)]  Compute the probability of no occurences in a one hour period?
\item[(b)]  What is the probability of two or more occurences in a one hour period?
\item[(c)]  Suppose $Y$ is a random variable that describes the amount of time between occurences. What probability distribution should be used to describe $Y$?
\end{itemize}
%Progress 9/15


\noindent (When answering, justify your answer with workings, or by reference to an
axiom, theorem or rule.)

\newpage

%-----------------------------------%
\subsection*{Question 5 Binomial Distribution [3 Marks] } % 12 Marks
A biased coin yields `Tails' on $45\%$ of throws. Consider an experiment that consists of throwing this coin 5 times.
\begin{itemize}
\item[(a)]  Evaluate the following term $^{5}C_3$.
\item[(b)]  Compute the probability of getting three `Tails' in this experiment.
\item[(c)]  Compute the probability of getting two `Heads' in this experiment.
\end{itemize}

\noindent(When answering, justify your answer with workings, or by reference to an
axiom, theorem or rule.)

\bigskip






%-----------------------------------%
\subsection*{Question 6 Exponential Distrbution [2 Marks]}
% Exponential [3 Marks]

Suppose an exponential random variable $X$ describes a ``lifetime" denominated in days, has a rate parameter of $\lambda = 1/7$
\begin{itemize}
\item[(a)]  What is the probability of a lifetime less than 5 days?
\item[(b)]  What is the probability of lifetime greater than 7 days?
\end{itemize}


\noindent(When answering, justify your answer with workings, or by reference to an
axiom, theorem or rule.)
\bigskip






%\subsection*{Q6. Poisson Distribution  }  % 14 Marks
%Suppose that a telephone help-line receives 4 calls per hour during offices hours.
%\begin{itemize}
%\item[a.]  Compute the value of $m$ for a 30 minute period during office hours.
%\item[b.]  Compute the probability of the help-line getting exactly one call in a 30 minute period during office hours.
%\end{itemize}
%\bigskip
%\subsection*{Q7. Exponential Distribution (1 Mark)} % 15 Marks


%\begin{itemize}

%\item[a.]  Compute the value of $P(X \leq 482)$

%\end{itemize}
