

\subsection*{Q1. Theory for Inference Procedures (4 Marks)}
Answer the four short questions. Each correct answer will be awarded 1 mark.
\begin{itemize}

\item  What is a $p-$value?

\item  Briefly describe how $p-$value is used in hypothesis testing

\item  What is meant by a Type I error?

\item   What is meant by a Type II error?
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\subsection*{Q2. Normal Distribution }
An analogue signal received at a detector (measured in microvolts), is normally distributed with a mean of 100 microvolts 
and a standard deviation of 25 microvolts.

\begin{itemize}

\item  What is the Z-score for 137.5 microvolts? 

\item  What is the Z-score for 80 microvolts?

\item  What is the probability that the signal will exceed 137.5 microvolts? 

\item[(iv)] What is the probability that the signal will be less than 80 microvolts?

\item   What is the probability that the signal will be between 80 and 125 microvolts?
\end{itemize}

%
\item[(iii)] What is the micro-voltage below which 25% of the signals will be? 
\item[(4 marks)]

\newpage
\subsection*{Q3. Inference Procedures (6 Marks)}


\textbf{Part A:} A sample of 200 voters was taken by a political pollster to estimate the proportion of first preference votes a 
particular candidate will obtain in a forthcoming election. 
It was found that 110 out of these 200 voters would give the candidate their first preference.


\begin{itemize}

\item  State the point estimate that would be used in an inference procedure.

\item  Compute the standard error that would correspond to the point estimate you have computed.

\item  Determine the 95\% confidence interval for your point estimate.
\end{itemize}

\noindent \textbf{Part B:} Using a significance level of 5\%, test the hypothesis that the percentage of voters who will give this 
particular candidate their first preference in the election is 60\%.{\tiny } 

\begin{itemize}

\item  Formally state the null and alternative hypotheses.

\item  Compute the Test Statistic for this hypothesis test.

\item  Given that the critical value is 1.96, state your conclusion for this test.
\end{itemize}

\end{document}