\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MA4413 2013} \rhead{Mr. Kevin O'Brien}
\chead{Midterm Assessment 2 }
%\input{tcilatex}

\begin{document}
\subsection*{Part 1. Theory for Inference Procedures (4 Marks)}
Answer the four short questions. Each correct answer will be awarded 1 mark. Reasonably short answers will suffice, i.e. your answers should not exceed a paragraph.
\begin{itemize}
\item  What is a $p-$value?
\item  Briefly describe how $p-$value is used in hypothesis testing
\item  What is meant by a Type I error?
\item   What is meant by a Type II error?
\end{itemize}
(Once you have completed this section, \textbf{please turn over.})
\newpage
\subsection*{Part 2. Normal Distribution (5 Marks)}
The strength of an analogue signal received at a detector (measured in microvolts : $\mu V$ ), is normally distributed with a mean of 100 $\mu V$  
and a variance of 100 $\mu V^2$ . 


\noindent With the signal strength denoted as $X$, we can say:

\[ X \sim N(100,100) \]

\begin{itemize}
\item  What is the Z-score for 115 $\mu V$ ? 
\item  What is the Z-score for 80 $\mu V$ ?
\item  What is the probability that the signal will exceed 115 $\mu V$ ? 
\item   Estimate the value of $z_o$, which is an observation from the Standard Normal (Z) distribution, given that:
\[  P(Z \geq z_o) = 0.04.\] 
(Hint: you may use a reasonable close value)
\item   What is the micro-voltage threshold $x_0$ below which 96\% of the signals will be? 
\[  P(X \leq x_o) = 0.96,\] 
\[  P(X \geq x_o) = 0.04.\]
%\item[(iii)] What is the micro-voltage below which 25\% of the signals will be?
%\item[(iv)](1 Mark) What is the probability that the signal will be less than 80 microvolts?
%\item[(v)]  What is the probability that the signal will be between 80 and 125 microvolts?
\end{itemize}
(Once you have completed this section, \textbf{please turn over.})
%\item[(iii)] What is the micro-voltage below which 25% of the signals will be? \item[(4 marks)]
\newpage
(\textbf{Room for Answers})
