
%====================================================================================================%






\chapter{Questions}
\section{Question D1 - Binomial Distribution } % 10 Marks
An inspector of computer parts selects a random sample of components
from a large batch to decide whether or not to audit the full batch.

%---------------------------------------------%
\begin{itemize}
\item[(i)] lf 20\% or more of the sample is defective, the entire batch is
inspected, Calculate the probability of this happening if it is
thought that the population contains 4\% defective components and
a sample of 20 is selected.
\item[(ii)] lf 10\% or more of the sample is defective, the entire batch is
inspected. Calculate the probability of this happening if it is
thought that the population contains 4\% defective components and
a sample of 50 is selected.
(10 marks)
\end{itemize}


\section{Question D2 - Binomial Distribution (2 Marks) } % 10 Marks
A biased coin yields `Tails' on $48\%$ of throws. Consider an experiment that consists of throwing this coin 11 times.
\begin{itemize}
\item[a.] (1 Mark) Evaluate the following term $^{11}C_2$.
\item[b.] (1 Mark) Compute the probability of getting two `Tails' in this experiment.
\end{itemize}
\section{Question D3 -  Poisson Distribution (2 Marks) }  % 12 Marks
Suppose that a telephone help-line receives 4 calls per hour during offices hours.
\begin{itemize}
\item[a.] (1 Mark) Compute the value of $m$ for a 30 minute period during office hours.
\item[b.] (1 Mark) Compute the probability of the help-line getting exactly one call in a 30 minute period during office hours.
\end{itemize}

%
%
% x=seq(2,18,length=1600)
% y=dnorm(x,10,2)
% plot(x,y,type="l",  col="black")
% x=seq(10,12.4,length=240)
% y=dnorm(x,10,2)
% polygon(c(10,x,12.4),c(0,y,0),col="wheat")
% abline(h=0)
% text(14,0.15,"P(10 < X < 12.4)")
%
%
%
%
% x=seq(2,18,length=1600)
% y=dnorm(x,10,2)
% plot(x,y,type="l",  col="black")
% L=2
% U=9.7
% x=seq(L,U,length=((U-L)*100) )
% y=dnorm(x,10,2)
% polygon(c(L,x,U),c(0,y,0),col="wheat")
% abline(h=0)
% text(14,0.15,"P(10 < X < 12.4)")
%
%
%abline(v=10)


\begin{itemize}
\item In a group of 24 adults, only 6 people watch televised pay to view
sports events. \item A visitor successively asks two people chosen at random from the
community whether they watch these TV programmes.
\item What distribution should be used in this instance? \item What is the probability
that the second person chosen does watch them?
\end{itemize}


%-------------------------------- %
\section{Probability Questions}

Question 1 

Combinations and Permutations: From first principles, compute the following:
1.5C2
2.4C0
3.4C4
4.10C1
5.10C0


%===============================================================%


Question 2

Six horses are entered in a race. Larry picks two of the horses at random, and bets on them. 
How many ways are there of picking two horses at random from six?





%===============================================================%

\subsection{Question 3}
A lot contains 13 items of which 4 are defective. Three items are drawn at random from the lot one after the other. Find the probability p that all three are non-defective.




%===============================================================%

\subsection{Question 5}

On completion of a programming project, four programmers from a team submit a collection of subroutines to an acceptance group. The following table shows the percentage of subroutines each programmer submitted and the probability that a subroutine submitted by each programmer will pass the certification test based on historical data.

ProgrammerABCD
Proportion of subroutines submitted0.100.200.300.40
Probability of acceptance0.550.600.950.75



%===============================================================%

\subsection{Question 5}
(i) What is the proportion of subroutines that pass the acceptance test?
(ii) After the acceptance tests are completed, one of the subroutines is selected at random and found to have passed the test. What is the probability that it was written by Programmer A?





%===============================================================%

\subsection{Question 6}
Two manufacturing plants produce similar parts. Plant A produces 1000 parts, 100 of which are defective. Plant B produces 2000 parts, 170 of which are defective. 

1.Present this information using a contingency table

2.A part is selected at random and found to be defective. What is the probability that it came from plant A ?







%===============================================================%


Question 5
Consider a binomial experiment where the number of independent trials is 10, and the probability of success is 0.25. Let X denote the number of successes in the 10 trials.
A)Write out the sample space of X.
B)For the each of the following events, write out the sample points:
i)the number of successes is less than or equal to 3,
ii)the number of successes is greater than 4, 
iii)the number of successes is greater than 8, 
iv)the number of successes is between 4 and 7 inclusive.


%===============================================================%

Question 6
By considering the relevant sample points from the sample space in the previous question, show that 
% 1)P(4 ≤X ≤8) = P(X ≤8) – P(X ≤3 ) = P(X  4) – P(X  9)
% 2)P(X=4) = P(X  4) – P(X  5 )
% 3)P(X≥7) = 1- P(X ≤6)
(i.e. show how the sample space can be partitioned accordingly)



%===============================================================%


