\section{Normal Distribution : Arab Horses Worked Example}
The mass of Arab horses is normally distributed with mean 900 lbs and standard deviation of 50lbs.
\begin{itemize}
	
	\item  Calculate the probability that an Arab horse weighs more than 940 lbs.
	\item Calculate the probability than an Arab horse weighs between 880 lbs and 960 lbs.
\end{itemize}

\noindent \textbf{Solution}\\

\begin{itemize}
	\item Let X be mass of Arab horses.
	
	\item We have to find $P(X\leq940)$.            (Remark "equality component" is included as a formality, but it is not important)
	
	
	\item	Find the Z value that corresponds to 940 
	
	\[Zo=\frac{Xo-\mu}{\sigma}= \frac{940 -900}{50}= 0.8\]
	
	\[P(X \leq 940) = P(Z \leq 0.8) \]
	
	
	\item		From Murdoch Barnes tables 3, we find that $P(Z \leq 0.8) = 0.2119$
\end{itemize}





Solution 

\[P ( 880 \leq X \leq 960).\]


What proportion of horses are between 880 lbs and 960 lbs?
\begin{itemize}
	\item Find out the probability of the complement event.
	\item The complement event is the combination of being too high  or too low for this interval.
	
	\item Inside interval $P ( 880 \leq X \leq 960).$
	
	\item Outside interval $P (X \leq 880) + P(X \geq 960)$
	
	\item Complement Rule $P ( 880\leq X \leq 960)  = 1 - [P (X\leq 880) +P(X\geq 960)]$
	
\end{itemize}



Find the probability of being too high?

\[Zo=\frac{Xo-\mu}{\sigma}= \frac{960 -900}{50}= 1.2\]

\[P(X \leq 960) = P(Z \leq 1.2) = 0.1151\]


Find the probability of being too low?
\[Zo= \frac{Xo-\mu}{\sigma}= \frac{880 -900}{50}= -0.4 \]
\[P(X \leq 880) = P(Z \leq -0.4)  \]

%------------------------------------------------------------- %
How to compute $P(Z \leq -0.4)$

Symmetry: 	$P(Z \leq -0.4)$ = $P(Z \geq 0.4)$ = 0.3446


\begin{itemize}
	\item Outside Interval = 0.4596        (0.3446 +  0.1151)
	\item Inside Interval = 0.5404
\end{itemize}



%------------------------------------------------------------- %
What weight is exceeded by 97.5\% of Arab horses?

Find Xo  such that P(XXo) = 0.975

\begin{itemize}
	\item 	P(Z1.96) = 0.025     [From Tables] 
	
	\item	P(Z-1.96) = 0.025  [Symmetry]
	
	\item	P(Z-1.96) = 0.975         
	
	\item	\[-1.96 = \frac{Xo- 900}{50} \]
	
	
	\item	Xo= 802 lbs  [Answer]
\end{itemize}	





%------------------------------------------------------------- %



%----------------------------------------------------------------%
\section{Worked Example 2 - with Solutions}
IQ scores are assumed to have a normal distribution with mean 100 and standard deviation 15.

\begin{itemize}
	\item What IQ would you have if you were in the 80th percentile?
	\item Estimate the threshold for the top 10 percent?
	\item What is the probability of having an IQ above 142?
	\item What is the probability of having an IQ below 97?
\end{itemize}

