
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{framed}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Worked Examples} \chead{Inference Procedures} %\input{tcilatex}

\begin{document}
\large 
\noindent An exercise physiologist wants to determine if several short bouts of exercise provide the same benefit for cardiovascular fitness as one long bout of exercise. \\
	\noindent 50 volunteers are randomly assigned to group 1 and do standardised aerobic exercise on a stationary bicycle for 30 minutes once a day, 5 days a week. 40 volunteers are randomly assigned to group 2 and do the same exercise for 10 minutes, 3 times a day, 5 days a week. Cardiovascular fitness was measured by VO2 max (maximum oxygen consumption while exercising). 
	\begin{framed}
	\begin{description}
		\item[Group 1] The mean change in VO2 after 12 weeks of exercise was 2.1 for group 1 with a standard deviation of 1.7.
		\item[Group 2] The mean change in VO2 after 12 weeks of exercise was 0.7 for group 2 with a standard deviation of 1. 
	\end{description}
	\end{framed}
	\noindent Test the hypothesis that there is no significant difference between two groups are the same. You may assume a 5\% level of significance.
	
\begin{enumerate}[(a)]
		\item Formally state your null and alternative hypotheses.
		\item Compute the test statistic.
		\item Discuss your conclusion to this test, supporting your statement with reference to appropriate values. You may assume a 5\% level of significance.
\end{enumerate}




\begin{framed}
		\noindent \textbf{Hypothesis Testing : Steps when using Critical Value approach}
		
		\begin{itemize}
			\item[1] Formally State the Null and Alternative Hypothesis \smallskip
			{
				\begin{itemize}
					\item[$\ast$] \textbf{ALWAYS} include a short written description of both hypotheses.
					\item[$\ast$] State hypotheses in mathematical notation where possible.
					
				\end{itemize}
			}
			\item[2] Calculate Test Statistic (TS) using relevant formulas.\smallskip
			\item[3] Determine the Critical Value (CV) from tables. \smallskip
			\item[4] By comparing the values of the Test Statistic and Critical Value, decide whether to reject the Null Hypothesis.
		\end{itemize}
	\end{framed}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statement of Hypotheses}
\noindent The first step in hypothesis testing is to specify the null hypothesis and an alternative hypothesis.
\begin{itemize}
    \item The Null Hypothesis ($H_0$) proposes that
    \item The Alternative Hypothesis ($H_1$) proposes that
\end{itemize}
\begin{description}
\item[$H_0$:] $\mu_1 = \mu_2$ ( The population means are equal)
\item[$H_1$:] $\mu_1 \neq \mu_2$ (The population means are different)
\end{description}

\noindent Equivalently, we can write the hypotheses in terms of difference between groups.
\begin{description}
\item[$H_0$:] $\mu_1 - \mu_2 = $ 
\item[$H_1$:] $\mu_1 - \mu_2\neq  = 0$ 
\end{description}



\noindent (Remark: Two Tailed Test, therefore $k = 2$, and $\alpha = 0.05$)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection*{Computing the Test Statistic}

\noindent \textbf{Standard Errors}
\begin{itemize}
    \item The Standard Error Formula are typically provided in the exam paper, or an accompanying document.
    \item Each type of test has a different Standard Error Formula.
\end{itemize}
\begin{framed}
 The relevant formula for the standard error is
\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{{s^2_1\over n_1}+{s^2_2 \over n_2}} \]
\end{framed}
\bigskip
\begin{itemize}
\item $s^2_1$ and $s^2_2$ is the variance of samples $1$ and $2$ respectively.
\item $n_1$ and $n_2$ is the sample size of both samples.\bigskip

\end{itemize}
\begin{eqnarray*}
 S.E(\bar{x}_1 - \bar{x}_2) &=& \sqrt{ \frac{1.7^2}{50} + \frac{1^2}{40} } \\
& & \\
&=& \sqrt{ 0.0578  + 0.0250}
& & \\
&=& \sqrt{ 0.0828}
& & \\
&=& 0.2877
\end{eqnarray*}
\end{eqnarray*}
\newpage 

\noindent \textbf{General Structure of the Test Statistic}\\
\noindent The Test Statistic $TS$ is a Normally  Distributed random variable with $TS \sim Z(0,1^2)$.
\begin{framed}
\[ TS = {\mbox{Point Estimate} - \mbox{Expected Parameter Value under $H_{0}$} \over \mbox{Std. Error}}\]
\end{framed}


\begin{eqnarray*}
TS &=& \frac{ 15\;-\; 0}{3.4234} \\
& & \\
&=& 4.3816\\
\end{eqnarray*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Determine the Critical Value}

\begin{itemize}
\item The critical value is determined from Statistical Tables.
\item Determination depends on the significance level $\alpha$, the sample size $n$ and the number of tails in the test (i.e. is it a one-tailed or two tailed test.
\end{itemize}

\noindent \textbf{Significance Level}

\begin{itemize}
\item In hypothesis testing, the significance level $\alpha$ is the criterion used for rejecting the null hypothesis. 
%\item The significance level of a statistical hypothesis test is a fixed probability of wrongly rejecting the null hypothesis $H_0$, if it is in fact true.
%\item Equivalently, the significance level (denoted by $\alpha$) is the probability that the test statistics will fall into the \textbf{\emph{critical region}}, when the null hypothesis is actually true. 

\item In University courses, common choices for $\alpha$ are $0.05$ and $0.01$. We will use $\alpha =0.05$ (i.e. 5\%).
\item We have a large aggregate sample size ($n_1 + n_2 > 30)$.
\item The hypothesis test is 2-tailed procedure.
\item The Critical Value is 1.96.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Decision}



\begin{framed}
\noindent \textbf{What are the conclusions}
	\begin{itemize} 
		
		\item[Yes:] We \textbf{reject the Null} Hypothesis. \\ \textit{We have sufficient evidence against Null Hypothesis.}
		
		\item[No:] We \textbf{fail to reject} Null hypothesis. \\ \textit{We do not have sufficient evident against Null Hypothesis.}
	\end{itemize}	
	{	\normalsize
		N.B. Note the terminology that we are using. Also note exactly what our conclusion is: We are talking about strength of evidence, rather than what is true or false.}
	
\end{framed}
	\smallskip
\begin{framed}
\begin{itemize}
	\item 	If $TS > CV$ , where $CV$ is a critical value corresponding to the sample size and confidence level, then reject the null hypothesis. 
	\item  If $TS \leq CV$ , we fail to reject the null hypothesis. i.e. Not enough evidence. 
	\end{itemize}	
\end{framed}	

\noindent Here $TS \leq CV$ , i.e. ($1.8758 \leq 1.96$), we fail to reject the null hypothesis. i.e. Not enough evidence of a difference. 
	
	
	
\end{document}	
