
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{framed}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Worked Examples} \chead{Inference Procedures} %\input{tcilatex}

\begin{document}
\large 
\noindent A pharmaceutical Company wants to test Dozenol, a new cold medicine intended
for night use. Tests for such products often include a “treatment group” of people
who use the drug and a “control group” of people who don’t use the drug. Fifty
people with colds are given Dozenol, and 100 others are not. The systolic blood
pressure is measured for each subject, and the sample statistics are given below.
\begin{center}
    \begin{tabular}{|c|c|} \hline
Dozenol & Control Group \\ \hline
$n_1 = 50$  & $n_2 = 100 $ \\ \hline
$\bar{x}_1 = 203.4$ & $\bar{x}_2 = 189.4$ \\ \hline
$s_1 = 39.4$  &  $s_2 = 39.0$ \\ \hline
\end{tabular}
\end{center}

\begin{enumerate}[(a)]
    \item Using a 0.05 level of significance, test the claim that Dozenol does not affect blood pressure. Clearly state your null and alternative hypotheses and your conclusion.
\end{enumerate}

\bigskip 

\begin{framed}
\noindent \textbf{Hypothesis Testing : Steps when using Critical Value approach}

\begin{itemize}
\item[1] Formally State the Null and Alternative Hypothesis \smallskip
{
\begin{itemize}
\item[$\ast$] \textbf{ALWAYS} include a short written description of both hypotheses.
\item[$\ast$] State hypotheses in mathematical notation where possible.

\end{itemize}
}
\item[2] Calculate Test Statistic (TS) using relevant formulas.\smallskip
\item[3] Determine the Critical Value (CV) from tables. \smallskip
\item[4] By comparing the values of the Test Statistic and Critical Value, decide whether to reject the Null Hypothesis.
\end{itemize}
\end{framed}
\newpage 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statement of Hypotheses}
\noindent The first step in hypothesis testing is to specify the null hypothesis and an alternative hypothesis.
\begin{itemize}
    \item The Null Hypothesis ($H_0$) proposes that the medication is not effective (i.e. make no difference in terms of blood pressure)
    \item The Alternative Hypothesis ($H_1$) proposes that the medication is effective. (It makes a significant difference in terms of blood pressure.)
\end{itemize}
\begin{description}
\item[$H_0$:] $\mu_1 = \mu_2$ (The population means are equal)
\item[$H_1$:] $\mu_1 \neq \mu_2$ (The population means are different)
\end{description}

\noindent Equivalently, we can write the hypotheses in terms of difference in means between the two groups.
\begin{description}
\item[$H_0$:] $\mu_1 - \mu_2 = 0$ 
\item[$H_1$:] $\mu_1 - \mu_2\neq  0$ 
\end{description}



\noindent (Remark: Two Tailed Test, therefore $k = 2$, and $\alpha = 0.05$)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection*{Computing the Test Statistic}

The point estimate is the difference in sample means:
    \[ \bar{x}_1 - \bar{x}_2 = 203.4- 189.4 = 14\]
    
\noindent \textbf{Standard Errors}
\begin{itemize}
    \item The Standard Error Formula are typically provided in the exam paper, or an accompanying document.
    \item Each type of test has a different Standard Error Formula.
\end{itemize}
\begin{framed}
 The relevant formula for the standard error is
\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{{s^2_1\over n_1}+{s^2_2 \over n_2}} \]
\end{framed}
\bigskip
\begin{itemize}
\item $s^2_1$ and $s^2_2$ is the variance of samples $1$ and $2$ respectively.
\item $n_1$ and $n_2$ is the sample size of both samples.\bigskip

\end{itemize}
\begin{eqnarray*}
 S.E(\bar{x}_1 - \bar{x}_2) &=& \sqrt{{(39.4)^2 \over 50}+{(39.0)^2 \over 100}}   \\
&=& \sqrt{{1552.36 \over 50}+{1521 \over 100}}   \\
&=& \sqrt{31.0472 + 15.21}  \\
&=& \sqrt{46.2572}  \\
&=& 6.801\\
\end{eqnarray*}
\newpage 

\noindent \textbf{General Structure of the Test Statistic}\\
\noindent The Test Statistic $TS$ is a Normally  Distributed random variable with $TS \sim Z(0,1^2)$.
\begin{framed}
\[ TS = {\mbox{Point Estimate} - \mbox{Expected Parameter Value under $H_{0}$} \over \mbox{Std. Error}}\]
\end{framed}


\begin{eqnarray*}
TS &=& \frac{ 14\;-\; 0}{6.801} \\
& & \\
&=& 2.0585\\
\end{eqnarray*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Determine the Critical Value}

\begin{itemize}
\item The critical value is determined from Statistical Tables.
\item Determination depends on the significance level $\alpha$, the sample size $n$ and the number of tails in the test (i.e. is it a one-tailed or two tailed test.
\end{itemize}

\noindent \textbf{Significance Level}

\begin{itemize}
\item In hypothesis testing, the significance level $\alpha$ is the criterion used for rejecting the null hypothesis. 
%\item The significance level of a statistical hypothesis test is a fixed probability of wrongly rejecting the null hypothesis $H_0$, if it is in fact true.
%\item Equivalently, the significance level (denoted by $\alpha$) is the probability that the test statistics will fall into the \textbf{\emph{critical region}}, when the null hypothesis is actually true. 

\item In University courses, common choices for $\alpha$ are $0.05$ and $0.01$. We will use $\alpha =0.05$ (i.e. 5\%).
\item We have a large aggregate sample size ($n_1 + n_2 > 30)$.
\item The hypothesis test is 2-tailed procedure.
\item The Critical Value is 1.96.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Decision}



\begin{framed}
\noindent \textbf{What are the conclusions}
\begin{itemize} 

\item[Yes:] We \textbf{reject the Null} Hypothesis. \\ \textit{We have sufficient evidence against Null Hypothesis.}

\item[No:] We \textbf{fail to reject} Null hypothesis. \\ \textit{We do not have sufficient evident against Null Hypothesis.}
\end{itemize}
{\normalsize
N.B. Note the terminology that we are using. Also note exactly what our conclusion is: We are talking about strength of evidence, rather than what is true or false.}

\end{framed}
\smallskip
\begin{framed}
\begin{itemize}
\item If $TS > CV$ , where $CV$ is a critical value corresponding to the sample size and confidence level, then reject the null hypothesis. 
\item  If $TS \leq CV$ , we fail to reject. null hypothesis. i.e. Not enough evidence. 
\end{itemize}
\end{framed}

\noindent Here $TS > CV$ , i.e. ($2.06\leq 1.96$), we can reject he null hypothesis. i.e. enough evidence of a significant difference. 



\end{document}
