\begin{itemize}
%--------------------------------- %

\item[(a)] \textbf{\textit{Normal Probability Distribution }}\\
A well known IT retailer has determined that the number of computer accessories sold, on a weekly basis in its largest 
shop, is normally distributed with a mean of 1000 and standard deviation of 50.
\begin{itemize}

\item  Estimate the proportion of weeks that the company will sell more than 950 products.


\item  Estimate the proportion of weeks that the company will sell less than 975 products.

\item  Estimate the proportion of weeks that the company will sell between 950 products and 1025 products?
\end{itemize}
%--------------------------------- %


\item[(b)] \textbf{\textit{Theory of Statistical Inference }}

\\Answer the following questions on the theory of statistical inference.
\begin{itemize}

\item  What is a $p-$value?

\item  Briefly describe how $p-$value is used in hypothesis testing.

\item  What is meant by a ``Type I error"?

\item   What is meant by a ``Type II error"?
\end{itemize}
%--------------------------------- %
\bigskip


\item[(c)] \textbf{\textit{Confidence Intervals (4 Marks)}}\\
A press release for a broadband provider stated that $90\%$ percent of customers are very satisfied
with the standard of service. To test this claim, the local chamber of commerce surveyed 110 randomly selected customers. 
Among the sampled customers, 89 stated that they are very satisfied.


%Test the hypothesis that $90\%$ of all customers are very satisfied with their service. You may assume a significance level of 5\%.



\begin{itemize}

\item  Compute the appropriate value for the standard error for a confidence interval.

\item  Compute the 95\% confidence interval for $\pi$, the true proportion.
%
\item[iii] (2 marks) For the test statistic, determine the corresponding p-value.

\item  What is your conclusion for this claim made by the press release? Justify your answer.
\end{itemize}
%--------------------------------- %
\end{itemize}
{
\normalsize
\textit{\textbf{Please turn over for the remaining sections of Question 3.}}
}
%
