
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{framed}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Worked Examples} \chead{Exponential Distribution} %\input{tcilatex}

\begin{document}
	
	\large 
	
	\section*{Exponential Distribution: Sample Question}
	
	In a large company computer network, there is an average of 40 log-ons to the network per hour. Suppose thet the average amount of time between log-ons is an exponential random variable.
	\medskip
	\begin{enumerate}[(a)]
		\item What is the average amount of time between log-ons?
		\item What is the probability that there will be no log-ons for at least 2.4 minutes
		\item What is the probability that the next log-on within 1 minutes of the last?
		\item What proportions of log-ons occur between 1 minutes and 2.4 minutes of the last log-on?
	\end{enumerate}
	
	\newpage 
	\subsection*{Solution to Part A }
	
	\large
	\begin{itemize} \item What is the average amount of time between log-ons?
		
		\item If there is 40 log-ons in 60 minutes, it is reasonable to think that someone logs on approximately every 1.5 minutes.
		\item Therefore $\mu = 1.5$
		\item Therefore the Poisson rate parameter is $\lambda= {1 \over 1.5}$ = 0.666
	\end{itemize}
	
	\newpage 
	\subsection*{Solution to Part B}
	
	
	What is the probability that there will be no log-ons for at least 2.4 minutes?\\
	
	\medskip 
	From the formulae:
	\[
	P( X \geq k) = e^{{-k \over \mu}} .
	\]
	\[
	P( X \geq 2.4) = e^{{-2.4 \over 1.5}} = e^{-1.6} = 0.2018.
	\]
	\medskip
	\begin{framed}
		\noindent \texttt{R} code 
		\begin{verbatim}
		> # Less than 2.4
		> pexp(2.4,rate=(2/3))
		[1] 0.7981035
		> 
		> # Greater than 2.4
		> pexp(2.4,rate=(2/3),lower=FALSE)
		[1] 0.2018965
		
		\end{verbatim}
	\end{framed}
	
	\newpage 
	\subsection*{Solution to Part C }
	
	
	
	What is the probability that the next log-on within 1 minutes of the last?\\
	i.e. $P(X \leq 1)$
	\bigskip
	From the formulae:
	\[
	P( X \leq 1) = 1 - e^{{-1 \over 1.5}} = 1 -  e^{-0.6666}
	\]
	
	\[
	P( X \leq 1) = 1 -  0.5135  = 0.4865
	\]
	\begin{framed}
		\medskip
		\noindent \texttt{R} code 
		
		\begin{verbatim}
		> pexp(1,rate=(2/3))
		[1] 0.4865829
		\end{verbatim}
	\end{framed}
	
	\newpage 
	\subsection*{Solution to Part D}
	
	
	
	What proportions of log-ons occur between 1 minutes and 2.4 minutes of the last log-on?
	
	\begin{itemize}
		\item \textbf{Too Low:} $P(X \leq 1) = 0.4865$
		\item \textbf{Too High:} $P(X \geq 2.4) = 0.2018$
		\item Probability of being inside interval $P(1 \leq X \leq 2.4) \approx 0.3117$.
		\item $P(1 \leq X \leq 2.4) = 1- ( 0.4865 + 0.2018) = 0.3117$
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%
	\newpage
	BLANK
	
	
\end{document}
