

\item 
A web-based software company claims that the average amount of time it takes for
online queries to be dealt with is less than 2 hours. Out of a sample of 15 queries, the
sample mean J? = 3.5 hours and the standard deviation is 30 minutes.
\begin{itemize}
	\item[(i)] Construct the null and alternative hypothesis statements.
	\item[(ii)] Test this claim using a significance level of 0.05.
	\item[(iii)] Describe the two types of errors associated with hypothesis testing and how
	they relate to this question?
\end{itemize}


\item 
A manufacturer of a common cold cure claims that the product provides
relief for 70\% of people who use it. ln a test of 400 people, it was found
that 300 people said the treatment provided relief.

\begin{enumerate}[(i)]
	\item Calculate a 95\% confidence interval for the true proportion of
	people who would get relief from the product.
	
	\item Suppose the manufacturer wishes to be 95\% confident that the
	prediction is correct to within 2\% of the true proportion. What
	sample size is needed?
	
	\item Using a significance level of 5\%, test the hypothesis that more than
	70\% of people who use the product find relief.\\ Clearly state your
	null and alternative hypotheses and your conclusion.
\end{enumerate}

\item 
A study was carried out to compare two treatments for the flu. A total of 500
newly diagnosed flu patients were randomly assigned to one of the two treatments.
\begin{itemize}
	\item Of the 280 assigned to the first treatment, 168 still had the flu after 2 days after
	diagnosis. \item Of the 220 assigned to the second treatment, 176 still had the flu after 2
	days after diagnosis. \end{itemize} Let $p_l$ denote the probability that a flu patient assigned to the
first treatment will still have the flu after 2 days after diagnosis; let $p_2$ denote the
corresponding probability for the second treatment.

\item 
A company organizes two evening courses, one on stock market trading and one on
spread-betting. From a sample of 100 clients, 64 of them choose the stock market course.

\begin{enumerate}[(i)]
	\item Calculate a 95\% confidence interval for the percentage of clients who
	prefer the stock market course. (5 marks)
	\item lt is known that in past years the percentage of clients who preferred the
	stock market trading classes was 75\%. Should the company conclude that
	the interest in the stock market trading courses has decreased significantly in
	comparison to past years? Clearly state $H_0$ and $H_1$.
\end{enumerate}

\begin{enumerate}[(i)]
	\item Provide an estimate of the difference between the population
	proportions (i.e. $\pi_l -\pi_2$).
	\item Calculate a 95\% confidence interval for the difference between the
	population proportions.
	\item Use a 0.05 significance level to determine if there is a difference
	between the two proportions. [Clearly state the null and alternative hypotheses
	and your conclusion].
\end{enumerate}
