
%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1 (a) Small Sample Hypothesis Test}
\large
\begin{itemize}
%\item The standard deviation of the life for a particular brand of ultraviolet tube is known to
%\item Also it is assumed, but not known, that the operating life of the tubes is normally distributed.

\item The manufacturer claims that average tube life for a particular brand of ultraviolet tube
is 9,000 hr. \item Test this claim at the 5 percent level of significance against the alternative hypothesis
that the mean life is not 9,000 hr \item We are given the following information:  a sample of $n = 10$ tubes the mean operating
life was $\bar{x} = 8,800$ hr. The sample standard deviation is be $s = 500$ hr.
%\item (Intuitively this would suggest a one-tailed test that the mean is less than 9000 hours)
\end{itemize}
\end{frame}


%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1 (b) }
\large
\begin{itemize}
\item $H_0 \mbox{ : } $ $\mu = 9000$ (Average life span is 9000 hours.)
\item $H_1 \mbox{ : } $ $\mu \neq 9000$ (Average life span is not 9000 hours.)
\end{itemize}
\bigskip
\begin{itemize}
\item The observed difference is -200 hours. (i.e. 8,800 - 9,000 hours)
\item The standard error is determined from formulae.
\[ S.E. (\bar{x}) = {s \over \sqrt{n}} = {500 \over \sqrt{10}}  = 158.1139 \]
\end{itemize}
\end{frame}
%--------------------------------------------------------------------------------------%
\begin{frame}[fragile]
\frametitle{Example 1 (c) : Test Statistic and Critical Value }
\large
\[ TS = \frac{8800 - 9000}{158.11} \]
\begin{itemize}
\item The test statistic $TS = -1.265$
\item The CV is determined with $\alpha = 0.05$ and $k = 2$ (column = $\alpha/k=0.025$).
\item The sample is small n = 10 $df = n-1 = 9$ (i.e. row =9).
\item Therefore $CV = 2.262$

\item (Remark: If the sample was large, we could use $CV = 1.96$).

\end{itemize}
\end{frame}

%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1 (d): Decision Rule }
\large
\begin{itemize}
\item \textbf{Decision:}Is $|TS| >CV$? Is $1.265 > 2.262$?
\item No. We fail to reject the null hypothesis. \item There is not enough evidence to say that the mean lifespan is not 9000 hours.
\end{itemize}
\end{frame}
%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example}
\large
\begin{itemize}
\item The standard deviation of the life for a particular brand of ultraviolet tube is known to be $s = 500$ hr,
\item Also it is assumed, but not known, that the operating life of the tubes is normally distributed. \item The manufacturer claims that average tube life
is at least 9,000hr. \item Test this claim at the 5 percent level of significance against the alternative hypothesis
that the mean life is less than 9,000 hr, and given that for a sample of $n = 10$ tubes the mean operating
life was $\bar{x}  =  8,800$ hr.
\end{itemize}
\end{frame}

%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example}
\large
\begin{itemize}
\item $H_0 \mbox{ : } $ $\mu \geq 9000$	Average life span is not less than 9000 hours.
\item $H_1 \mbox{ : } $ $\mu < 9000$    Average life span is  less than 9000 hours.
\end{itemize}
\bigskip
\begin{itemize}
\item The observed difference is -200 hours. (i.e. 8,800 - 9,000 hours)
\item The standard error is determined from formulae.
\[ S.E. \bar{x}  = {s \over \sqrt{n}} = {500 \over \sqrt{10}} \]
\end{itemize}
\end{frame}

%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example}
\large
\begin{itemize}
\item The CV is determined from Murdoch Barnes Table 7, with $\alpha = 0.05$ and $k = 1$.
\item The sample is small n= 10  $df = n-1 = 9$.Therefore CV = 
\item (Remark: If the distribution was known to be normal, we could use $df = \infty$, i.e $CV = 1.645$).
\item Decision rule : Is $|TS| >CV$? Yes. 
\end{itemize}
\end{frame}

%--------------------------------------------------------------------------------------%
\end{document}