Q. 5) \item Define an ARCH model and explain what particular properties of the model would
make it appropriate for modelling a time series asset.

Consider the time series
ğ‘Œô€¯§=0.1 +0.4Yt-1 +0.9et-1 +et
Where et is white noise process with variance Ïƒ2
\item Identify the model as an ARIMA(p,d,q) Process (1)
\item Determine whether ğ‘Œô€¯§ is
a) A stationary process
(1)
IAI CS2A-0921
Page 6 of 8
b) An invertible process (1)
\item Calculate E(ğ‘Œô€¯§ ) and find auto co-variance function for ğ‘Œô€¯§ 
\item Determine that MA(âˆ) representation for ğ‘Œô€¯§ 
[17]



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Solution 5:
i)
An ARCH(p) model is ğ‘‹ğ‘¡=ğœ‡+ğ‘’ğ‘¡âˆšğ›¼0+Î£ğ›¼ğ‘˜(ğ‘‹ğ‘¡âˆ’ğ‘˜âˆ’ğœ‡)2ğ‘ğ‘˜=1
Where et are independent (0,1)
2 Marks for writing the equation correctly and explaining the terms
For an asset with price Zt above model is used to to model Ln(Zt/Zt-1 )
ï‚· It can be seen that a large departure in Xt-k from Î¼ will result in Xt having a larger variance. This will then result in a large volatility for the asset price.
ï‚· This behaviour is observed in actual practice as the volatility of the price of a particular asset is much higher following a significant change in the price of the asset.
ï‚· Therefore ARCH model is more appropriate to model such asset class.
(4)
Consider the time series
ğ‘Œğ‘¡=0.1 +0.4Yt-1 +0.9et-1 +et
Where et is white noise process with variance Ïƒ2
ii)
The model is ARIMA(1,0,1) if Yt is stationary
(1)
(ii)
iii)
a) The characteristic polynomial for the AR part is A(z) = 1 âˆ’ 0.4z the root of which has absolute value greater than 1 so the process is stationary.
b) The characteristic polynomial for the MA part is B(z) = 1 + 0.9z the root of which has absolute value greater than 1 so the process is invertible.
(1)
(1)
(iii)
iv)
Since the process is stationary we know that E(Yt ) is equal to some constant Î¼ independent of t.
Taking expectations on both sides of the equation defining Yt gives
E(Yt ) = 0.1 + 0.4E(Ytâˆ’1)
Î¼ = 0.1 +0.4Î¼
Î¼ = 0.1/( 1 0.4) = 0.1666666
Note that
Cov(Yt , et ) = Cov(0.1 + 0.4Yt-1 + 0.9et-1 + et , et )
=0.4Cov(Yt-1, et ) + 0.9Cov(et-1, et ) + Cov(et , et ) = 0 + 0 + Ïƒ2 = Ïƒ2
Similarly
IAI CS2A-0921
Page 5 of 8
Cov(Yt ,et-1) =0 + 0.4Cov(Yt-1, et-1) + 0.9Cov(et-1, et-1) + Cov(et ,et-1) = 0.4Ïƒ2 + 0.9Ïƒ2 + 0 = 1.3Ïƒ2
So
Î³0 = Cov(Yt , Yt ) = Cov(Yt , 0.1 + 0.4Yt-1 + 0.9et-1 + et )
= 0.4Î³1 + 0.9 Ã— 1.3Ïƒ2 + Ïƒ2 = 0.4Î³1 + 2.17Ïƒ2 -----------------(1)
And
Î³1 = Cov(Yt-1, Yt ) = Cov(Yt-1, 0.1 + 0.4Yt-1 + 0.9et-1 + et )
= 0.4Î³0 + 0.9Ïƒ2---------------------------------------------------------------------- (2)
Substituting for Î³1 in (1) gives
Î³0 = 0.4 Ã— 0.4Î³0 + 0.4 Ã— 0.9Ïƒ2 + 2.17Ïƒ2 = 0.16Î³0 + 2.53Ïƒ2
Î³0 = (2.53 /0.84 )Ïƒt62 = 3.011905Ïƒ2
Substituting into (2) gives
Î³1 = 0.4 Ã— 3.011905Ïƒ2 + 0.9Ïƒ2 = 2.104762Ïƒ2
And in general
Î³s = 0.4Î³sâˆ’1 for s â‰¥ 2
So Î³s = 0.4s-1 Ã— 2.104762 Ïƒ2.
(6)
(iv)
v)
We have (1âˆ’0.4ğµ)ğ‘Œğ‘¡=0.1+0.9ğ‘’ğ‘¡âˆ’1+ğ‘’ğ‘¡
Hence ğ‘Œğ‘¡= (1âˆ’0.4ğµ)âˆ’1(0.1+0.9ğ‘’ğ‘¡âˆ’1+ğ‘’ğ‘¡) = Î£0.4ğ‘–ğµğ‘–âˆğ‘–=0(0.1+0.9ğ‘’ğ‘¡âˆ’1+ğ‘’ğ‘¡)
=0.11âˆ’0.4+0.9Î£0.4ğ‘–ğ‘’ğ‘¡âˆ’ğ‘–âˆ’1+Î£0.4ğ‘–ğ‘’ğ‘¡âˆ’ğ‘–âˆğ‘–=0âˆğ‘–=0 =0.16667+ğ‘’ğ‘¡+1.3Î£0.4ğ‘–âˆ’1ğ‘’ğ‘¡âˆ’ğ‘–âˆğ‘–=1
(4)
[17 Marks]

