Q. 1) Answer the following Questions
\item The Pareto Distribution is
a. Negatively skewed always
b. Sometimes positively skewed, sometimes negatively skewed. It depends on mean and
median of the distribution.
c. Positively skewed always
d. None of the above

\item Claims from a particular portfolio are normally distributed with mean 800 and
standard deviation 100. An individual excess of loss arrangement with retention limit
800 is in place. Insurer’s mean claim payment net of reinsurance is
a. 783.130
b. 547.278
c. 235.855
d. None of the above
(3)
\item Claims arising from a certain type of insurance policy are believed to follow an
exponential distribution. The lower quartile claim is 250. The mean claim size is
a. 695.210
b. 869.015
c. 180.337
d. 509.520

\item Consider the following Health (H), Sickness (S), Death (D) model with the addition
of an extra ‘Terminally ill’ state (T). The rates associated with different transitions are
as follows.
What is the expected future life time of a healthy life? (Choose the closest value)
a. 10.5 years
b. 11 years
c. 12 years
d. 12.5 years
e. 14 years

H S
D T
0.03
0.20
0.50
0.08
0.05
0.75
IAI CS2A-0921
Page 3 of 8
\item The number of cars that enter the parking area of a shopping complex are modelled as
a Poisson process with a rate 40 per hour. What is the probability that 5 cars enter in
first 15 minutes and then another 4 cars enter in next 15 minutes?
a. 0.072%
b. 3.783%
c. 1.892%
d. 0.291%
e. Less than 0.001%
(3)
\item In a certain village, the electric fittings go out of order as soon as there is excessive
usage of electricity. The probability of such event happening over a day is 20%. The
village has to spend the night in darkness. To fix the electricity, an engineer from the
Government agency is called the next day. There is only 75% probability that he is
able to fix the electricity the same day. If he is unable to fix, he comes again the next
day and tries to fix. The process is repeated till he is able to fix.
Calculate the long term probability that the village has to see dark nights. Select from the
correct options below:
a. 23%
b. 77%
c. 50%
d. 21.05%
e. 78.95%

\item The diagrams below show four Markov chains, where the arrows represent a nonzero
transition probability
1) Markov Chain 1
2) Markov Chain 2
IAI CS2A-0921
Page 4 of 8
3) Markov Chain 3
4) Markov Chain 4
Based on the above, select the correct option
a. None of the four chains are Irreducible
b. Only Markov chains 1,2 and 3 are Irreducible
c. Only Markov chains 1 and 2 are Irreducible
d. Only Markov chains 2 and 3 are Irreducible
e. All four Markov chains are Irreducible

[20]

Solution 1:
i)
Answer: C
(2)
ii)
Answer: D
(3)
iii)
Answer: B
(2)
iv)
Answer: C
(4)
v)
Answer: A
(3)
vi)
Answer: D
(4)
vii)
Answer: C
(2)
[20]

