
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{framed}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{StatsResource} \rhead{Worked Examples} \chead{Inference Procedures} %\input{tcilatex}

\begin{document}
\large 
%====================================================%
\noindent 
A study was carried out to compare two treatments for the flu. A total of 500
newly diagnosed flu patients were randomly assigned to one of the two treatments.
\begin{itemize}
\item Of the 280 assigned to the first treatment, 168 still had the flu after 2 days after
diagnosis. \item Of the 220 assigned to the second treatment, 176 still had the flu after 2
days after diagnosis. 
\end{itemize} 

% Let $p_l$ denote the probability that a flu patient assigned to the
% first treatment will still have the flu after 2 days after diagnosis; let $p_2$ denote the
% corresponding probability for the second treatment.

\begin{enumerate}[(a)]
\item Test the hypothesis that the 2 day recovery rate is the same for treatment groups. Clearly state your null and alternative hypotheses and your conclusion. Use a significance level of 5\%.
\end{enumerate}

\bigskip

\begin{framed}
\noindent \textbf{Hypothesis Testing : Steps when using Critical Value approach}

\begin{itemize}
\item[1] Formally State the Null and Alternative Hypothesis \smallskip
{
\begin{itemize}
\item[$\ast$] \textbf{ALWAYS} include a short written description of both hypotheses.
\item[$\ast$] State hypotheses in mathematical notation where possible.

\end{itemize}
}
\item[2] Calculate Test Statistic (TS) using relevant formulas.\smallskip
\item[3] Determine the Critical Value (CV) from tables. \smallskip
\item[4] By comparing the values of the Test Statistic and Critical Value, decide whether to reject the Null Hypothesis.
\end{itemize}
\end{framed}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statement of Hypotheses}


\begin{itemize}
\item The Null Hypothesis ($H_0$) proposes that there is no difference in the 2 day recovery rates between the two types of treatments
\item The Alternative Hypothesis ($H_1$) proposes that there is a difference in the 2 day recovery rates between the two types of treatments.
\end{itemize}
\begin{description}
\item[$H_0$:] $\pi_1 = \pi_2$  - i.e. Population proportions are equal to each other.
\item[$H_1$:] $\pi_1 \neq \pi_2$ - i.e. Population proportions are different to each other.
\end{description}

\noindent Equivalently, the hypotheses can be expressed in terms of difference in proportions.
\begin{description}
\item[$H_0$:] $\pi_1 - \pi_2 = 0$ - i.e. Difference in population proportions is zero.
\item[$H_1$:] $\pi_1 - \pi_2 \neq 0$ - i.e. Difference in population proportions is not zero.
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection*{Computing the Test Statistic}

\noindent \textbf{Point Estimate}

\begin{itemize}
 \item For those who have NOT recovered within 2 days - the sample proportions for both groups are
\[ \hat{p}_1 = \frac{168}{280} = 0.60 \;\;(\mbox{i.e.}\; 60\%) \] 
\[ \hat{p}_2 = \frac{176}{220} = 0.80 \;\;(\mbox{i.e.}\; 80\%) \]  
\item For those who have recovered within 2 days - the sample proportions for both groups are
\[ \hat{p}_1 = \frac{112}{280} = 0.40 \;\;(\mbox{i.e.}\; 40\%) \] 
\[ \hat{p}_2 = \frac{44}{220} = 0.20 \;\;(\mbox{i.e.}\; 20\%) \]  
\item The point estimate is the difference between these proportions:
\[ \hat{p}_1  - \hat{p}_2  = 0.20 \;\;(\mbox{i.e.}\; 20\%) \]
\end{itemize}

\noindent \textbf{Standard Errors}
\begin{itemize}
\item The Standard Error Formula are typically provided in the exam paper, or an accompanying document.
\item Each type of hypothesis test has a different Standard Error Formula.
\end{itemize}
\bigskip
\begin{framed}
\noindent \textbf{Standard Error for Difference in Proportions}\\
\noindent {Two large independent samples}
\begin{eqnarray*}
S.E.(\hat{P_1}-\hat{P_2})&=&\sqrt{ \bar{p}\times(1-\bar{p}) \times \left(\frac{1}{n_1}+\frac{1}{n_2}\right)}.\\
\end{eqnarray*}
\begin{itemize}
\item $\bar{p}$ is the overall proportion
\[\bar{p} = \frac{x_1 + x_2}{n_1+n_2}\]
\end{itemize}
\end{framed}

\[\bar{p} = \frac{x_1 + x_2}{n_1+n_2} = \frac{168 + 176}{280+ 220} = \frac{344}{500} =0.688\]

\noindent Using percentages, the aggregate proportion is 68.8\%.

\begin{eqnarray*}
S.E.(\hat{P_1}-\hat{P_2})&=&\sqrt{ 68.8 \times 31.2 \times \left(\frac{1}{280}+\frac{1}{220}\right)}.\\
&=&\sqrt{ 2146.56 \times 0.00811}.\\
&=&\sqrt{17.4086}\\
&=& 4.1723 \\
\end{eqnarray*}
\noindent \textbf{General Structure of the Test Statistic}

\noindent The Test Statistic $TS$ is a Normally  Distributed random variable with $TS \sim Z(0,1^2)$.
\begin{framed}
\[ TS = {\mbox{Point Estimate} - \mbox{Expected Parameter Value under $H_{0}$} \over \mbox{Std. Error}}\]
\end{framed}


\begin{eqnarray*}
TS &=& \frac{ 20\;-\; 0}{4.1723} \\
& & \\
&=& 4.7935\\
\end{eqnarray*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Determine the Critical Value}

\begin{itemize}
\item The critical value is determined from Statistical Tables.
\item Determination depends on the significance level $\alpha$, the sample size $n$ and the number of tails in the test (i.e. is it a one-tailed or two tailed test?)
\end{itemize}

\noindent \textbf{Significance Level}

\begin{itemize}
\item In hypothesis testing, the significance level $\alpha$ is the criterion used for rejecting the null hypothesis. 
%\item The significance level of a statistical hypothesis test is a fixed probability of wrongly rejecting the null hypothesis $H_0$, if it is in fact true.
%\item Equivalently, the significance level (denoted by $\alpha$) is the probability that the test statistics will fall into the \textbf{\emph{critical region}}, when the null hypothesis is actually true. 

\item In University courses, common choices for $\alpha$ are $0.05$ and $0.01$. We will use $\alpha =0.05$ (i.e. 5\%).
\item We have a large aggregate sample size ($n_1 + n_2 > 30)$.
\item The hypothesis test is 2-tailed procedure.
\item The Critical Value is 1.96.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\subsection*{Decision}



\begin{framed}
\noindent \textbf{What are the conclusions}
\begin{itemize} 

\item[Yes:] We \textbf{reject the Null} Hypothesis. \\ \textit{We have sufficient evidence against Null Hypothesis.}

\item[No:] We \textbf{fail to reject} Null hypothesis. \\ \textit{We do not have sufficient evident against Null Hypothesis.}
\end{itemize}
{\normalsize
N.B. Note the terminology that we are using. Also note exactly what our conclusion is: We are talking about strength of evidence, rather than what is true or false.}

\end{framed}
\smallskip
\begin{framed}
\begin{itemize}
\item If $TS > CV$ , where $CV$ is a critical value corresponding to the sample size and confidence level, then reject the null hypothesis. 
\item  If $TS \leq CV$ , we fail to reject. null hypothesis. i.e. Not enough evidence. 
\end{itemize}
\end{framed}
\smallskip
\noindent Here $TS > CV$ , i.e. ($4.79 > 1.96$), so we reject the null hypothesis. i.e. evidence of a significant difference. 

%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
BLANK

\end{document}
