\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{Maths Resource} \rhead{Tutorial Sheet B} \chead{Hypothesis Testing} %\input{tcilatex}
\begin{document}
\section*{Hypothesis Testing : Tutorial Sheet C}
\begin{enumerate}

\item 
An IT competency test, used for staff recruitment, is devised so as to give a normal distribution of scores with a mean of 100. A random sample of 49 experienced IT users  who are given the test achieve a mean score of 121 with a standard deviation of 14. 

\begin{enumerate}[(a)]
\item	Perform a hypothesis test to assess whether this group of IT Users is unusual (i.e. have a different mean from the general population).
\item	Compute a 95\% confidence interval for the group.
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item  
A claim has been made that the mean body temperature of healthy adults is equal to 98.6 degrees. 
A sample of 106 people has produced a mean body temperature of 98.2 degrees and a standard deviation of 0.62. Test the claim using a 5\% significance.

\item 
A manufacturer of computer monitors  has for many years used a process giving a mean life of 4700 hours and a standard deviation of 1460 hours. 
A new process is tried to see if it will increase the life significantly. A sample of 100 monitors gave a mean life of 5000 hours.  
Does the new process make a difference at the 5\% level of significance?

\item In a study of store checkout scanners, 1234 items were checked and 20 of them were overcharges.
Use a 5\% significance level to test the claim that with scanners, 1\% of sales are overcharges.




\item The average height of a sample of 16 students was 173cm with a variance of 144cm$^2$. The average height of the Irish population is 169cm. 
\begin{enumerate}[(a)]
\item Can it be stated at a significance level of 5\% that students are on average taller than the population as a whole? 
\item What assumption is used to carry out this test? Is this assumption reasonable?
\end{enumerate}


%----------------------------------------------------------------------- %
\item 
The average mass of a sample of 64 Irish teenagers (Let say - 18 year old males) was 73.5kg with a variance of 100kg$^2$. 
The average mass of an equivalent sample of 81 Japanese teenagers was 68.5kg with a variance of 81 kg$^2$. 
\begin{enumerate}[(a)]
\item Test the hypothesis that Irish students are larger (in terms of mass) than Japanese teenagers.
\item By calculating the appropriate $p-$value, test the null hypothesis that the mean mass of all Irish students is 70kg at significance levels of 5\%. 
\item Using the appropriate confidence interval, test the hypotheses that the average mass of all Irish students is a) 70kg, b) 72kg, c) 75kg at a significance level of 5\%.
\end{enumerate}


% \textbf{\textit{Standard Error Formula}}
% \[ S.E.(\bar{x}_1 - \bar{x}_2)  = \sqrt{\frac{s_1^2}{n_1} + \frac{s_2^2}{n_2}} \]
% \[ S.E.(\bar{x}_1 - \bar{x}_2)  = \sqrt{\frac{10^2}{64} + \frac{9^2}{81}}  = \sqrt{2.56} = 1.6\]
% \newpage


\item A study was carried out in which researchers collected crime data. Of those convicted of
arson, 50 were drinkers and 43 abstained. Of those convicted of fraud, 63 were drinkers and 144
abstained. Use a 0.01 level of significance to test the claim that the proportion of drinkers among
convicted arsonists is greater than the proportion of drinkers convicted of fraud.



