

%--------------------------------------------------------------------- %
%Question 4 

% Accuracy Precsion and Recall (7 Marks)
% Two Sample Hypothesis test for Sample Proportions (8 Marks)
% Confidence Interval (5 Marks)

%--------------------------------------------------------------------- %
\newpage
\section*{Question 4 }
%\subsection*{Question 4.  }

\begin{itemize}

\item[(a)] \textbf{\textit{Binary Classification }}\\
For following binary classification outcome table, calculate the following appraisal metrics.
\begin{itemize}	

\item 	accuracy;

\item 	recall;

\item 	precision;

\item  	F-measure.
\end{itemize}	

\begin{center}
\begin{tabular}{|c|c|c|}
\hline  & \phantom{spa}Predict Negative\phantom{spa} & \phantom{spa}Predict Positive\phantom{spa} \\ 
\hline\phantom{spa} Observed Negative \phantom{spa}&	9530	&	10	\\ 
\hline \phantom{spa}Observed Positive\phantom{spa} & 	300	&	160	\\ 
\hline 
\end{tabular} 
\end{center}

\begin{itemize}	

\item   Explain why the F-measure is considered a more informative measure of performance than the Accuracy score.

\end{itemize}

\item[(b)] \textbf{\textit{Inference Procedures (10 Marks)}}\\
Two IT training companies, \textit{XtraTech} and \textit{YourSkills}, offer an exam preparation course for a well-known computer industry certification. 
A study was carried out to compare the results from the most recent group of students from both companies.
\begin{itemize}

\item[$\bullet$]30 students from the \textit{XtraTech} course have completed the test. The average score for these students was 910 marks with a standard deviation of 48 marks.


\item[$\bullet$]25 students from the \textit{YourSkills} course have completed the test. Their average score was 950 marks with a standard deviation of 42 marks.
\end{itemize}

Test the hypothesis that the both sets of students perform equally well on average. You may use a significance level of 5\%. You may assume that both samples are normally distributed and have equal variance.
%\end{itemize}
\begin{itemize}

\item  Formally state the null and alternative hypotheses for this procedure.

\item  Compute the point estimate for the difference in means of the results from both courses.

\item  Compute the appropriate value for standard error for this test. Clearly show your workings.

\item   Compute the test statistic.

\item   What is your conclusion for this procedure?
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%